Title

### 2020-08-11 paper.tex
Add beginning of section 3

	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.\todo{Describe his derivations here, based on Green's function methods \& can generalise to strong-coupling and magnetic impurities}
	Assuming no magnetic impurities and weak coupling, his expressions reduce to
	\begin{equation}
		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
	\end{equation}
	with
	\begin{align}
		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
	\end{align}

@@

	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence.
	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}
\begin{itemize}
	\item Limitations on superconducting dielectric function.
	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
	\item Include description of cutoff process.
	\item Include description of the interpolation process.
	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
	It might be too obvious that the convergence is expected because these are real quantities.
	\item Any other potentially interesting approximations?
	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
\end{itemize}

>>>>

	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.\todo{Describe his derivations here, based on Green's function methods \& can generalise to strong-coupling and magnetic impurities}
	Assuming no magnetic impurities and weak coupling, his expressions reduce to
	\begin{equation}
		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right], \label{eq:eps}
	\end{equation}
	with
	\begin{align}
		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
	\end{align}

@@

	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence, a feature shared by similar expressions in \cite{AGD}.
	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}, this must be corrected to prevent divergences.
	For sufficiently large momenta, the response function should approach the normal state function\todo{add good ref of this}.
	Moreover, $\Im \epsilon$ should go to $0$ when $k \gtrapprox 2 \vf$, as otherwise there will be no available states within the Fermi surface for energy transfer (for more on this point, see the discussion in~\cite{FetterWalecka}).

	In order to account for the first point, for the normal state we can use the Lindahrd dielectric function, which has the correct nonlocal behaviour to describe the low $z$ noise\cite{QubitRelax}.
	The

\begin{itemize}
	\item Include description of cutoff process.
	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
	It might be too obvious that the convergence is expected because these are real quantities.
	\item Any other potentially interesting approximations?
	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
\end{itemize}
